Capstone Movielens Report

### 2025-05-26 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
RMD report:  UMGYE Model completed (minor fix).

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script.
:::

>>>>

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
:::
